### 2017-12-22 README.Rmd
update biometrika link in readme

`drtmle` is an R package that computes marginal means of an outcome under fixed
levels of a treatment. The package computes targeted minimum loss-based (TMLE)
estimators that are doubly robust, not only with respect to consistency, but
also with respect to asymptotic normality, as discussed in [Benkeser, et al (2017)](https://doi.org/10.1093/biomet/asx053). This property
facilitates construction of doubly-robust confidence intervals and hypothesis
tests.

>>>>

`drtmle` is an R package that computes marginal means of an outcome under fixed
levels of a treatment. The package computes targeted minimum loss-based (TMLE)
estimators that are doubly robust, not only with respect to consistency, but
also with respect to asymptotic normality, as discussed in [Benkeser, et al (2017)](https://academic.oup.com/biomet/article-abstract/104/4/863/4554445). This property
facilitates construction of doubly-robust confidence intervals and hypothesis
tests.
